---
title: "Topological neutrality"
author: "Jonathan Bourne"
date: "30 January 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


---
title: "Untitled"
author: "Jonathan Bourne"
date: "7 January 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This code explores the effect of what is removed on the amount of overloads/islands/targeted on the system

#Setup Block

```{r}

packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr","foreach", "doMC",  "xtable", "geomnet", "ggnetwork", "rlang", "animation", "ggridges", "poweRlaw", "Rtsne", "caret", "ranger", "xtable", "broom", "modelr", "yardstick", "sf", "rgdal", "foreach", "doMC")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


sapply(packages, library, character.only = TRUE)


lapply(packages, library, character.only = TRUE)
library(PowerGridNetworking)

select <- dplyr::select

#Set up file system to read the correct folders this switches between aws and windows mode

basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
datafile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ETYSAppendixB"
#LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Proportional Line Limits" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
#Functions <-"/home/jonno/Create_ETYS_network/Functions"
Tariff <- file.path(basewd,"Tariff and Transport")
PLwd <- "/media/jonno/Seagate Expansion Drive/Innoculation"
Saved_Sims <- file.path(PLwd, "Saved_Sims")
Deletion_Order_Folder <-  file.path(PLwd, "DeletionOrder") #Only one of the deletion order folders is needed. Either Nodes or Edges
Deletion_Order_Folder <- file.path(PLwd, "DeletionOrder_Nodes")
StratAttackWd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading/StratAttack"

source("/home/jonno/Create_ETYS_network/SubCode/LoadData2.R")


#FOr NetSci
#FiguresFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/NetSci2018 Poster/Figures"
```

#Create the Attack Orders
```{r}
#Set the path to a large enough storage
setwd(PLwd)

#Ensure there is powerflow
g <- PowerFlow(gbase, "FECK40")

g %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label=NA)

NetworkStats(g) %>%
  xtable() %>% print(type = "latex", file = file.path(FiguresFolder, "NetworkStats.txt"))

AttackRounds <- 1000

#Create a reproducible attack order
seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 100)  
saveRDS(DeleteOrders, filename)
}

```

#Set alpha colour gradient
```{r}
  AlphaGrad <-scale_colour_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))),
                          name = expression(alpha*" level")) #"Alpha value"
```




#Scramble Node function
```{r}
NodeCharacteristiceScrambler <- function(g, Sims, seed = 1983){
#This function generates a matrix that gives the new node function order.
  #for example it says that node 1 now has the function of node 5.
  #It simply generates an integer dataframe giving the new node function for each simulation
  #g: an Igraph object
  #Sims: the number of simulations
  
TotNodes <- vcount(g)
NodeNames <- tibble(name = get.vertex.attribute(g, name = "name"))

set.seed(seed)
Out <- 1:Sims %>%
    map(~{

      df <- sample(1:TotNodes, TotNodes, replace = FALSE) %>%
        as.matrix(., ncol = 1) %>%
        as_tibble() %>%
        setNames(paste0("Sim_", .x))
      return(df)
    }) %>%
    bind_cols(NodeNames, .)

}

ReOrderGraph <- function(g, Sim_Order){

  g2 <-g
  
    for(n in c("Demand", "Generation", "BalencedPower")){
      g2 <- set.vertex.attribute(g2, n, 
                                value = get.vertex.attribute(g2, n )[Sim_Order])
    }
  
  return(g2)
}

```



```{r}

seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 100)  
saveRDS(DeleteOrders, filename)
}

#Make simulations order
NewFunctionOrder <- NodeCharacteristiceScrambler(gbase, 100)
  
```

##Generate Stategies
```{r}

CreateStrategyAttackDf <- function(g){

ElecCen1<- ElectricalCentrality(g)
#degree
StratAttackVect <- c(as_data_frame(g, what = "vertices") %>% 
  as_tibble %>%
      mutate(metric = degree(g)) %>%
      arrange(desc(metric)) %>% .$name,
#entropic degree line limit
as_data_frame(g, what = "vertices") %>%
      mutate(metric = EntropicDegree(g, Scale = TRUE)) %>%
      arrange(desc(metric)) %>% .$name,
#entropic degree powerflow
as_data_frame(g, what = "vertices") %>%
      mutate(metric = EntropicDegree(g, value = "PowerFlow", Scale = TRUE)) %>%
      arrange(desc(metric)) %>% .$name,

#Electrical centrality
ElecCen1$NodeEC %>% arrange(-NodeEC) %>% .$Bus.Name,

#centrality
 as_data_frame(g, what = "vertices") %>%
      mutate(metric = betweenness(g)) %>%
      arrange(desc(metric)) %>% .$name
) %>% matrix(., nrow = 5, byrow = T) %>%
  as_tibble %>%
  mutate(SimulationID = paste0("Simulation_ID_",1:5)) %>%
  select(SimulationID, everything()) %>%
  setNames(c("SimulationID", paste0("Target", 1:vcount(g))))

return(StratAttackVect)

}


```

#Simulate attacks using strategies
```{r}
setwd(file.path(PLwd, "Scramble", "Strategy"))

for(n in 1:(ncol(NewFunctionOrder)-1)){
 
 Sim_Order<- NewFunctionOrder  %>% select(-1) %>% pull(n)
  
  g <- ReOrderGraph(gbase, Sim_Order)
  #calculate Flow
  g <- PowerFlow(g, "FECK40")
  #Make edges proportional to flow
  g<- Proportional_Load(g, alpha = 5)
  
  folder <- paste0("Order_", n)
  
    if(!file.exists(folder)){
      dir.create(folder)
    }
  
  StratAttackVect <- CreateStrategyAttackDf(g)

SaveMultiAttacks(g,  StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
}

```

#Extract data for scrambles

```{r}
ExtractAttackStats("/media/jonno/Seagate Expansion Drive/Innoculation/Scramble/Strategy", file.path(PLwd, "Attack_Strategy_SummaryData"))


AttackRoundData <- list.files(path = file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading","SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  filter(alpha == "alpha_value_500") %>%
  mutate(Strategy = "RandomAttack",
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup %>%
  SummariseMultiAttack %>%
  mutate(PercNum = NodesAttacked/958)


AttackStratRoundData <- list.files(path = file.path(PLwd,"Attack_Strategy_SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  mutate(Strategy = case_when(
    simulationID == "1" ~"Degree" ,
    simulationID == "2" ~"EntDeg_LinkLimit",
    simulationID == "3" ~"EntDeg_PowerFlow",
    simulationID == "4" ~"Elec_Centrality",
    TRUE ~ "Centrality"
  ),
  simulationID = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.),
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked, alpha) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup


SummaryofGC<- AttackStratRoundData %>%
  SummariseMultiAttack %>%
  mutate(PercNum = NodesAttacked/958) %>%
  bind_rows(AttackRoundData)

 NodeCollapse <- rbind(SummaryofGC %>%
  select(PercNum, mean, Strategy, GC05, GC95, sd, NodesAttacked) %>% mutate(type = "Giant componant size reduction"),
SummaryofGC %>% 
  select(PercNum, mPGfract, Strategy, PG05, PG95, sdPGfract, NodesAttacked) %>% 
  mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95, sd = sdPGfract)
) %>% mutate(Target = "Node") 

test <- NodeCollapse %>% #need to remove infinte values 
    filter(is.finite(mean), PercNum < 0.5)  


#This shows that the strategy attack on random orders is more aggressive than the random attack on the true order but not much more than that
 test %>% 
  filter(Strategy != "RandomAttack")  %>%
  ggplot(aes(x = PercNum, y =  mean, group = Strategy)) + 
  geom_line(aes(colour = Strategy), show.legend = TRUE) +
  geom_line(data =  test %>% 
  filter(Strategy == "RandomAttack") , aes(colour = 'Real'), color = 'black', linetype ="longdash") +
    facet_grid(~type)

```

#Plot the mean difference between strategies with random nodes and the true order
```{r}


AttackStratRoundData2 <- list.files(path = file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading","Attack_Strategy_SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  mutate(simulationID = case_when(
    simulationID == "1" ~"Degree" ,
    simulationID == "2" ~"EntDeg_LinkLimit",
    simulationID == "3" ~"EntDeg_PowerFlow",
    simulationID == "4" ~"Elec_Centrality",
    TRUE ~ "Centrality"
  ),
  alpha1 = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.)/100,
alpha = alpha %>%
  str_replace_all(., "_", " ") %>%
  str_extract_all(., "([aA-zZ\\s])+", T) %>%
  paste0(., ifelse(is.na(alpha1), "", alpha1)),
  alpha = fct_relevel(alpha, "alpha value 5", after=2) %>%
  fct_relevel(., "alpha value 2", after=2) %>%
  fct_relevel(., "alpha value 1.5", after=2),
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked, alpha) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup %>%
  filter(alpha == "alpha value 5") %>%
  mutate(Strategy = simulationID, 
         simulationID = 1)



test <- NodeCollapse %>%
  filter(type != "Giant componant size reduction") %>%
  left_join(AttackStratRoundData2) %>%
  mutate(meanDiff = mean -Blackout,
         meanRatio = mean/Blackout)

test %>%
  filter(!is.na(MaxComp)) %>%
   ggplot(aes(x = PercNum, y =  meanDiff, group = Strategy)) + 
  geom_line(aes(colour = Strategy), show.legend = TRUE) +#
  labs(title = "Mean difference from the True node function")

#
test %>%
  filter(Strategy != "RandomAttack") %>%
  select(PercNum, mean, Strategy, Blackout) %>%
  gather(key = "type", value = "value", -Strategy, -PercNum) %>%
  ggplot(aes(x = PercNum, y = value, colour = type)) + 
  geom_line() + 
  facet_wrap(~Strategy)


RandomStratScrambleData <- AttackStratRoundData %>%
  mutate(type = "Scramble") %>%
  bind_rows(., AttackStratRoundData2 %>% mutate(type = "Original",
                                               simulationID = 1e6)) 

#A lot of simulations go through a rapid network collapse after having a relatively linear period of growth
RandomStratScrambleData %>%
#  select(PercNum, mean, Strategy, Blackout) %>%
  ggplot(aes(x = PercNum, y = Blackout, colour = type, group = simulationID)) + 
  geom_line() +
  facet_wrap(~Strategy)+
  labs(x = "Percentage of nodes Attacked", title = "Comparing scrambled networks with the real network using different strategies")

#A density plot of the end point shows that there is a tendency to to collapse early
test2 <- RandomStratScrambleData %>%
  group_by(simulationID, Strategy) %>%
  summarise(NodesAttacked = max(NodesAttacked),
            PercNum = max(PercNum))
test2 %>%
  ggplot(aes(x = NodesAttacked, colour = Strategy)) + geom_density()
  

test2 <- AttackStratRoundData %>%
  left_join(., AttackStratRoundData2 %>% select(NodesAttacked, Strategy,  BlackoutTRUE = Blackout, GCTRUE = GCfract), by = c("NodesAttacked", "Strategy"))

SimEval <- expand.grid(unique(test2$Strategy), unique(test2$simulationID)) %>%
  map2_df(.x = .$Var1, .y = .$Var2, .f = ~{
    
  Temp <-  test2 %>%
  filter(Strategy== .x, simulationID==.y) %>%
    select(Blackout, BlackoutTRUE) %>% 
    filter(complete.cases(.))
  metrics(Temp, truth = BlackoutTRUE, estimate = Blackout) %>% 
    select(metric = .metric, estimate = .estimate) %>%
  #  spread(key = metric, value = estimate) %>%
    mutate(Strategy = .x, SimulationID = .y)
    
  })


#There is substantial difference between the strategies
SimEval %>%
  filter(metric != "mae") %>%
  ggplot(aes(x = Strategy, y = estimate, fill = Strategy)) + geom_boxplot()+
    facet_wrap(metric~., ncol = 1, scales = "free_y") +
  theme(legend.position="none")

```


#Extract Scramble graph vulnerability metrics

```{r}
NewFunctionOrder <- NodeCharacteristiceScrambler(gbase, 100)

StratScrambleVuln <- 1:100 %>% map_df(~{
 
  print(.x)
 Sim_Order<- NewFunctionOrder  %>% select(-1) %>% pull(.x)
  
  g <- ReOrderGraph(gbase, Sim_Order)
  #calculate Flow
  g <- PowerFlow(g, "FECK40")
  #Make edges proportional to flow
  g <- Proportional_Load(g, alpha = 5)

  tibble(
    Order = .x,
    name = get.vertex.attribute(g, "name"),
    #Elec_Centrality = ElectricalCentrality(g)$NodeEC,
       Degree = degree(g),
       Centrality  = betweenness(g, normalized = TRUE),
       EntDeg_LinkLimit = EntropicDegree(g, Scale = TRUE),
       EntDeg_PowerFlow = EntropicDegree(g, value = "PowerFlow", Scale = TRUE),
    Generator = get.vertex.attribute(g, "Generation")>0 | get.vertex.attribute(gstandard, "Demand")<0,
    Demand = get.vertex.attribute(g, "Demand")>0
       ) %>%
    left_join(.,  ElectricalCentrality(g)$NodeEC %>% 
                rename(Elec_Centrality = NodeEC, name = Bus.Name))

}) %>% mutate( Transfer = !(Generator |Demand),
       NodeType = case_when(
         Transfer ~ 1, #If transfer is true the node type is transfer
         Demand ~ 2, #if case a is flase but Demand is TRUE then the type is DEmand
         TRUE ~ 3
       ))


saveRDS(StratScrambleVuln, file.path(PLwd, "StratScrambleVuln.rds"))
#readRDS(file.path(PLwd, "StratScrambleVuln.rds"))

test <- StratScrambleVuln %>%
 select(GroupVar = Demand, Degree:EntDeg_PowerFlow, Elec_Centrality)

test %>%
  ggplot(aes(x = GroupVar, y = Elec_Centrality)) + geom_boxplot()

2:ncol(test) %>% map_df(~{
  
  Temp <- test %>%
  select(GroupVar, target = .x) %>%
  filter(is.finite(target))
  
  
  Temp %>%
  group_by(GroupVar) %>%
  summarise(counts = n(),
            mean = mean(target),
            median = median(target),
            sd = sd(target)) %>%
    mutate(
      SignifDiff = t.test(Temp$target[Temp$GroupVar], Temp$target[!Temp$GroupVar])$p.value<0.05,
      type = names(test)[.x])
})


test2 <- t.test(Temp$target[Temp$GroupVar], Temp$target[!Temp$GroupVar])

 gstandard <- PowerFlow(gbase, "FECK40")

 StandardVuln <- tibble(
    Order = 1e5,
    name = get.vertex.attribute(gstandard, "name"),
    #Elec_Centrality = ElectricalCentrality(gstandard)$NodeEC,
       Degree = degree(gstandard),
       Centrality  = betweenness(gstandard, normalized = TRUE),
       EntDeg_LinkLimit = EntropicDegree(gstandard, Scale = TRUE),
       EntDeg_PowerFlow = EntropicDegree(gstandard, value = "PowerFlow", Scale = TRUE),
    Generator = get.vertex.attribute(gstandard, "Generation")>0 | get.vertex.attribute(gstandard, "Demand")<0,
    Demand = get.vertex.attribute(gstandard, "Demand")>0,
    Transfer = !(Generator |Demand),
       NodeType = case_when(
         Transfer ~ 1, #If transfer is true the node type is transfer
         Demand ~ 2, #if case a is flase but Demand is TRUE then the type is DEmand
         TRUE ~ 3
       )) %>%
    left_join(.,  ElectricalCentrality(gstandard)$NodeEC %>% 
                rename(Elec_Centrality = NodeEC, name = Bus.Name))
 
 
test <- StandardVuln %>% mutate(Real = 1) %>%
  bind_rows(StratScrambleVuln%>% mutate(Real = 0)) %>%
  mutate_all(function(Var){ifelse(is.finite(Var), Var, 0)}) %>%
 select(NodeType, Degree:EntDeg_PowerFlow, Elec_Centrality, Real) %>%
  gather(key = "Metric", value = "value", -NodeType, -Real) %>%
  mutate( NodeType = case_when(
        NodeType== 1 ~ "Transfer", #If transfer is true the node type is transfer
        NodeType== 2 ~"Demand", #if case a is flase but Demand is TRUE then the type is DEmand
         TRUE ~ "Generator"
       ))


#How the real and synthetic nodes vary
#why is there any difference between synth nodetypes? shouldn't they all be the same?
test %>%
 # filter(Metric == "Degree", Real==1) %>% 
  ggplot(aes(x = NodeType, y = (value), fill = as.factor(Real))) + geom_boxplot() +
  facet_wrap(~Metric, scales = "free_y" )

test %>%
  filter(Metric == "Degree") %>% 
  group_by(NodeType,  Real) %>%
  summarise(mean = mean(value)) %>%
  spread(key = NodeType, value = mean)

test %>%
  mutate(Real = factor(Real)) %>%
  filter(Metric == "EntDeg_PowerFlow") %>%
  ggplot(aes(x = value, colour = Real)) + geom_density() +
  facet_wrap(~Metric, scales = "free_x") +scale_x_log10()
 
```


#Lost in scramble 

The amount of edges and nodes that are lost are quite small so I am not that botheres about correcting for it.
```{r}

EdgesNodesScramble <- 1:100 %>% map_df(~{
 
  print(.x)
 Sim_Order <- NewFunctionOrder  %>% select(-1) %>% pull(.x)
  
  g <- ReOrderGraph(gbase, Sim_Order)
  #calculate Flow
  g <- PowerFlow(g, "FECK40")
  #Make edges proportional to flow
  g <- Proportional_Load(g, alpha = 5)
  
  UselessEdge <- (get.edge.attribute(g, "PowerFlow")==0)

  print(get.edge.attribute(g, "name", index = (1:length(UselessEdge))[UselessEdge]) )
  #Remove Edges that are not doing anything and then any islanded nodes.
  #This is done before the simulation begins
  g <- delete.edges(g, (1:length(UselessEdge))[UselessEdge]) %>%
    BalencedGenDem(., "Demand", "Generation")

  tibble(Edges = ecount(g),
         Nodes = vcount(g),
         components = components(g)$no,
         Order = .x) 

})



EdgesNodesScramble %>%
  ggplot(aes(x = Edges)) + geom_density()

EdgesNodesScramble %>%
  ggplot(aes(x = Nodes)) + geom_density()


```

#Model Nodes

```{r}
KfoldIndex <- function(df, k = 10, seed = 2018){
  #Stratified kfold sampler
  #takes a 1 column dataframe which should be split into k-folds, returns a 1 column data frame where each row contains
  #an integer that represents the fold
  AddKFold<- function(df, k, seed){
    set.seed(seed)
    df %>% 
      mutate(fold_ID = rep(1:k, length.out = nrow(df)) %>%
               sample(., size = nrow(df)))}
  
  ColumnName <- names(df)[1]
  
  df <- df %>% select(Y = 1) %>%
    mutate(ID_for_sampling = 1:n())
  
  
  Pos <- df %>% 
    filter(Y == TRUE) %>% AddKFold(., k, seed)
  
  Neg <- df %>% 
    filter(Y == FALSE) %>% AddKFold(.,k, seed)
  
  df <- bind_rows(Pos, Neg) %>%
    arrange(ID_for_sampling) %>%
    select(fold_ID) %>% setNames(ColumnName)
  
  return(df)
}

```


This section classifies nodes as Using transfer/Load/Gen
```{r}

#Creates 10 fold classification to predict the rol of each node as a binary classifier
 RangerPerf <-c("Generator", "Demand", "Transfer", "NodeType") %>% map_df(~{
 StandardVuln2 <- StandardVuln %>%
  select(GroupVar = .x, Degree:EntDeg_LinkLimit) %>% #Using pure topology
  #select(GroupVar = .x, Degree:EntDeg_PowerFlow, Elec_Centrality) %>% #using extended topo, e.g. cheating
  mutate(GroupVar = GroupVar*1) %>%
  mutate_all(function(Var){ifelse(is.finite(Var), Var, 0)})


trainset <- StandardVuln2 %>%
  filter(complete.cases(.)) 

folds <- trainset %>%
  select(GroupVar) %>%
  KfoldIndex(., 10)

test <- 1:10 %>% map_df(~{

Mod <- ranger(data = trainset[folds !=.x,],  dependent.variable.name = "GroupVar", classification = TRUE)

Preds<- predict(Mod, trainset[folds==.x,])

ModConf <- confusionMatrix(factor(Preds$predictions, levels = c(1,0)), factor(trainset$GroupVar[folds==.x], levels = c(1,0)))

 ModPerf <- tibble(name = c(names(ModConf$overall),names(ModConf$byClass)), 
                   value = c(ModConf$overall, ModConf$byClass), fold = .x)

 return(ModPerf)
}) %>% spread(key = name, value = value) %>%
  mutate(Type = .x)

})


RangerPerf %>%
  ggplot(aes(x = Type, y = Accuracy-AccuracyNull)) + geom_boxplot()

#these nodes are at the end of a thread but are neither generation or load... why?
test <- StandardVuln %>%
  filter(Transfer==TRUE, Degree==1) %>%
  left_join(trans1 %>% select(name = Bus.Name, Generation = BusTransferB))

#About 35% of the nodes at the end of a line that are transfer nodes are in fact small generators
table(test$Generation==0)

```


```{r}

TestOut <- c("Generator", "Demand", "Transfer") %>%
  map_df(~{
    
StandardVuln %>%
  rename(target = .x) %>%
  group_by(Degree, target) %>%
  summarise(counts = n()) %>%
  mutate(target = ifelse(target, "true", "false")) %>%
  spread(key = target, value = counts, fill = 0) %>%
      ungroup %>%
  mutate(PercOfNodes = true/(true+false),
         PercofTot = true/sum(true),
         cumsum = cumsum(PercofTot),
         Type = .x)
    
  })

TestOut %>%
  group_by(Type) %>%
  summarise(counts = sum(true))

TestOut %>%
  ggplot(aes(x = Degree, y = cumsum, colour = Type)) + geom_line()

StandardVuln %>%
  ggplot(aes(x = Degree)) + geom_histogram(binwidth = 1)



```

#Scramble the Non-Transfer Nodes
Scramble the non transfer nodes and see what happens to the collapse pattern
If it is similar more similar to the real values, this means that the positioning of the nodes is not so important only that they are not transfer.

Otherwise I should scramble Gen and Demand internally and see what happens. 

The key is to understand what is happening in terms of placement of node and gen and use this to inform either a predictive or generative algorithm
